Designing and Developing a Personalised Recommender System

### 2021-02-08 paper/paper.tex
implemented item-based CF but takes ages
filtering restaurants into 12 categories

\subsection{Data preparation and feature selection}
Prepare data
Of the 209,393 businesses in the dataset, 168,903 are still open. 
There are 43,980 restaurants which are open and contain 'Restaurant' as one of the categories. 
502 businesses in the overall dataset don't list anything in their categories section. 
43,052 businesses had at least 1 check-in. 
There are 4,223,201 reviews of restaurants. 
695,951 tips for these restaurants. 
1,968,703 users. 
43,992 restaurants listed with covid features, 8 restaurants which make up 12 duplicate entries 
(8 have 2 entries and 4 have 3 entries), the only difference between their entries being in the 
"Virtual Services Offered" section. 
Allow to pick user ID of 10 users with most reviews made, to avoid cold start problem
4 users have over 10,000 reviews, the most is 14,455 (Victor, 8k3aO-mPeyhbR5HUucA5aA). 
I actually want to select the most reviews of the places I am accepting, restaurants. 
When taking the most reviews of restaurants in teh dataset, a threshold of 600 reviews gives a list of 10 users, 
with the most being 1747. 
I then checked each of these for how many different restaurants they had reviewed and the greatest number of times 
they had reviewed a single restaurant to check that none of them were just users who reviewed a small number of 
restaurants a huge amount of times each. 
All 10 users passed this criteria, with even the least active user having reviewed 496 unique restaurants, which will 
certainly avoid any cold-start problems. 
I split the businesses into 10 groups, by the city which they are closest to, I did this by using latitude and 
longitude rather than State or City since this does not give actual distance and restaurants close to a border 
could then be mis-categorised. 
The entire Yelp dataset is huge and much of it is not necessary for my domain of bars.
As such I prepared the data by eliminating any data not relevant to my domain.
I selected features such as user ratings and a particular user's average rating,
since if a user typically rates places they go highly, but rates a particular bar low,
this is more significant than a user who always rates places low.

\subsection{Hybrid scheme}
Which two algorithms
A hybrid scheme is a good way to design a recommender system, since you can get the
best of both algorithms if done properly.
Meaning better recommendations than either algorithm could achieve individually.

\subsection{Recommendation techniques/algorithms}
The first recommender system is collaborative filtering.
I am using item-based collaborative filtering, since the number of users is larger than the number of items 
(1,968,703 users vs 209,393 businesses in the entire dataset), this gives greater accuracy of predictions. 
In this case the list of available items does not change, so a user-based method would be unnecessary. 
One of the requirements for this system is justifiability, and item-based methods make it much easier to 
explain why certain predictions were made. 
I am using a weighted mixed combination of these two systems in order to produce the results
of my hybrid recommender system.

>>>>

\subsection{Data preparation and feature selection}
Prepare data
Of the 209,393 businesses in the dataset, 168,903 are still open. 
There are 43,965 restaurants which are open and contain 'Restaurants' as one of the categories. 
I then picked the top 12 most popular categories of restaurant: American, Mexican, Italian, Chinese, 
Seafood, Japanese, Canadian, Mediterranean, Indian, Thai, Middle Eastern, Vietnamese (in that order). 
When filtered for restaurants which fall into at least one of these categories, 
20,565 had at least one check-in in 2019
There are 2,956,316 reviews of these restaurants. 
481,073 tips for these restaurants. 
1,968,703 users. 
None of these restaurants are temporarily closed according to the covid features data. 
20,573 restaurants listed with covid features, 4 restaurants which make up 8 duplicate entries 
(4 have 3 entries), the only difference between their entries being in the 
"Virtual Services Offered" section. 
Allow to pick user ID of 10 users with most reviews made, to avoid cold start problem
4 users have over 10,000 reviews, the most is 14,455 (Victor, 8k3aO-mPeyhbR5HUucA5aA). 
I actually want to select the most reviews of the places I am accepting, restaurants. 
When taking the most reviews of restaurants in teh dataset, a threshold of 600 reviews gives a list of 10 users, 
with the most being 1747. 
I then checked each of these for how many different restaurants they had reviewed and the greatest number of times 
they had reviewed a single restaurant to check that none of them were just users who reviewed a small number of 
restaurants a huge amount of times each. 
All 10 users passed this criteria, with even the least active user having reviewed 496 unique restaurants, which will 
certainly avoid any cold-start problems. 
I split the businesses into 10 groups, by the city which they are closest to, I did this by using latitude and 
longitude rather than State or City since this does not give actual distance and restaurants close to a border 
could then be mis-categorised. 
Since there are 4,223,201 reviews of restaurants I filtered them by removing any which had zero 'useful' votes. 
When filtered to reviews with at least 1 'useful' vote, there are 1,735,732 and when at least 2 votes, 836,929
At least 3 votes, 462,412, at least 5 votes 190,902. 
51,737 with at least 10 votes

Top categories: American, Mexican, Italian, Chinese, Seafood, Japanese, Canadian, Mediterranean, Indian, Thai, Middle Eastern, Vietnamese

The entire Yelp dataset is huge and much of it is not necessary for my domain of bars.
As such I prepared the data by eliminating any data not relevant to my domain.
I selected features such as user ratings and a particular user's average rating,
since if a user typically rates places they go highly, but rates a particular bar low,
this is more significant than a user who always rates places low.

\subsection{Hybrid scheme}
Which two algorithms
A hybrid scheme is a good way to design a recommender system, since you can get the
best of both algorithms if done properly.
Meaning better recommendations than either algorithm could achieve individually.
Meta-level HRS with collaborative and content-based, or 
Cascade with knowledge-based and collaborative
Feature Augmentation with Knowledge Based and Collaborative

\subsection{Recommendation techniques/algorithms}
The first recommender system is collaborative filtering.
I am using item-based collaborative filtering, since the number of users is larger than the number of items 
(1,968,703 users vs 209,393 businesses in the entire dataset), this gives greater accuracy of predictions. 
In this case the list of available items does not change, so a user-based method would be unnecessary. 
One of the requirements for this system is justifiability, and item-based methods make it much easier to 
explain why certain predictions were made. 
Item-item collaborative filtering looks for restaurants that are similar, in terms of how people rate them, 
to the restaurants that the user has already rated and recommend the most similar restaurants. 
Filtering reviews by city and then using CF won't work because the active user may not have ever reviewed a restaurant 
in that city, so there is no way to assess similar restaurants to ones they have already rated. 
Instead I carried out CF on all high quality reviews and produce an ordering of recommendations, which I then filter 
by city.

I am using a weighted mixed combination of these two systems in order to produce the results
of my hybrid recommender system.
